Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

\subsection{Data Analysis}
In order to perform the analysis, we had to fill in training and testing matrices which contained play counts for user and song pairs. We did a random selection of data elements to split between the training (80\%) and testing (20\%) sets.

@@

The MAP@500 scores were computed by calculating the precision between a list of recommendations for a user and that user's test set. Specifically, we calculate the average precision at each element in the list of recommended items (i.e. percentage of correct items among first k recommendations) and sum these up for the first 500 recommendations (i.e. try for each $k \epsilon {1, ..., 500}$).
We then averaged the score over all users. Intuitively, the score looks at the percentage of recommendations that were in-line with the test set of songs actually listened to but also takes order into account. So it is preferable to recommend the songs in the user's test set earlier in the list of 500. Basically, the MAP score is similar to AUC of the ROC curve discussed in class except it takes ordering of the recommendations into account.

>>>>

\subsection{Data Analysis}
In order to perform the analysis, we had to fill in training and testing matrices which contained play counts for user and song pairs. We did a random selection of data elements to split between the training (80\%) and testing (20\%) sets. Next, we implemented various algorithms on the dataset in order to recommend songs to users, including matrix factorization, user-based collaborative filtering, and item-based collaborative filtering.

@@

Specifically, we used MAP@500 scores which take into account the first 500 recommendations given to each user. Generally, the score looks at the precision between a list of recommendations for a user and that user's test set. This was done by calculating the average precision at each element in the list of recommended items (i.e. percentage of correct items among first k recommendations) and averaging these for the first 500 recommendations (i.e. for each $k \epsilon {1, ..., 500}$, calculate the precision and average them together).
We then averaged the score over all users. Intuitively, the score looks at the percentage of recommendations that were in-line with the test set of songs actually listened to but also takes order into account. So it is preferable to recommend the songs in the user's test set earlier in the list of 500. The MAP score is similar to the AUC of the ROC curve discussed in class except it takes ordering of the recommendations into account, which is an important factor to consider in a recommendation system.
